Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-15 paper/v2/paper-edited.tex
5

Policies for (distributed) control planes differ from data-plane
policies in a few important ways. First, control-plane
policies must account for all failures at compile time; there is
no controller at runtime, so the routers must be configured in advance to handle failures in a compliant manner.
%
In \sysname, we enable such specifications through a notion of {\em path preferences}, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
%
Second, paths in a control-plane policy may be under-specified (e.g.,
"prefer customer" does not indicate a concrete path). The \sysname
compiler treats such under-specifications as constraints on the set of
allowed paths and automatically computes valid sets based on the topology.
%

In the rest of this section, we define \sysname policies for the two
examples from the previous section, introducing key aspects of
the \sysname language along the way. The complete syntax of the
language as well as our strategy for compiling \sysname policies to
BGP is defined in \S\ref{sec:compilation}.

@@

\sysname allows operators to configure the network with the
abstraction that they have centralized control over routing.
Specifically, the operator simply provides a set of high-level constraints
that describe the
different routes traffic may (or may not) take and their relative preferences.
\sysname specifications are written modularly via a series
of declarations.
%These definitions allow users to express the three
%major elements of any \sysname specification:  \emph{prefixes},
%\emph{paths} and \emph{policies}.
For example, to begin specification of the backbone
network from the previous section, we first express the idea that
we prefer that traffic leave the network through \CD{R1} over \CD{R2} (to \CD{Cust}) over \CD{Peer} over \CD{Prov} (policy P3 from Figure~\ref{fig:example1}):
%\begin{lstlisting}[mathescape=true]
%define ExitCust = $exit(R_1 \gg R_2)$
%\end{lstlisting}
\begin{code}
\Define Prefs = \Exit(R1 \Prefer R2 \Prefer Peer \Prefer Prov)
\end{code}
This  statement defines a set of \emph{ranked paths}, which includes
all paths (and only those paths) for which traffic exits our network
through either router \CD{R1}, router \CD{R2}, \CD{Peer}, or \CD{Prov}.
The paths that exit through \CD{R1}
are preferred (\Prefer) to those that exit through \CD{R2}, which are preferred to those that
leave through \CD{Peer} and then \CD{Prov}.  As we
describe in the next section, the \Exit\ predicate, as well as other
path predicates used later in this section, is simply a shorthand for
a particular regular expression over paths that is expressible in our policy
language. The preference operator (\Prefer) is flexible and can be used between constraints as well as among individual routers. For example, the above constraint could have been written equivalently as
\Exit(\CD{R1}) \Prefer \ldots \Prefer ~\Exit(\CD{Prov})

@@

\begin{code}
\Define NoTrans =
  \{\True \Path \NOT{}transit(Peer,Prov) \AND
           \NOT{}cust-transit(Cust,Prov)\}
\end{code}
\noindent
The \CD{NoTrans} constraint requires that all traffic not follow a path that transits the network between \CD{Peer} and \CD{Prov}.
Additionally, it prevents traffic from ever following paths that leave our network and later go through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
%
%% \begin{lstlisting}[mathescape=true]
%% Routing $\AND$  NoTransit
%% \end{lstlisting}
%
These constraints capture the entire policy. From them, \sysname will generate per-device import and export filters, local preferences,
MED attributes, and community tags to ensure that the policy is
implemented correctly under all failures.

@@

In our data center,
there are three main concerns:
(1) traffic for the prefix block allocated to each top-of-rack router must be able to reach that router,
(2) local services must not leak outside the data center, and
(3) aggregation must be performed on global prefixes to reduce churn
in the network.

\sysname allows us to specify each of these constraints modularly. The first constraint is about prefix ownership---namely, we only want traffic for certain prefixes to end up at a particular location. The following definition captures this intent.

@@

\begin{code}
\Define Ownership =
    \{PG1 \Path \End(A)
     PG2 \Path \End(B)
     PL1 \Path \End(E)
     PL2 \Path \End(F)
     \True \Path \End(\Out)\}
\end{code}
\noindent
In English: traffic for prefix \CD{PG1} is only allowed to follow paths that
end at router \CD{A}; traffic matching \CD{PG2},
but not \CD{PG1}, must
end at router \CD{B}; and so on.
Any traffic destined for a prefix that not a part of the data center should be allowed to leave the data center and end at some external location, which is otherwise unconstrained.
The special keyword \Out{} here matches any location outside the user's network, while the keyword \In{} will match any location inside the network.
For the second constraint, we can define another policy:

%% \begin{lstlisting}[mathescape=true]
%% define Routing = {
%%     $\path{p_{g*}}{any}$
%%     $\path{p_{l*}}{\NOT enter(out)}$
%%     $\path{true}{exit(out)}$
%% }
%% \end{lstlisting}
\begin{code}
\Define Locality =
    \{PL1 \OR PL2 \Path \textbf{only}(\In)\}
\end{code}
\noindent
%The first line states that there is no restriction (\Any)
%on how traffic must traverse the network for global prefixes.
%aside from the default restriction
%that traffic must not pass through the user's network and then loop
%back on itself.
%This means traffic for
%\CD{PG*} may be sent either from other data center routers or
%from external ASes.
The locality constraint ensures that traffic for local
prefixes only ever follows paths that are internal to the network at each hop.
This constraint guarantees that the services remain reachable only to locations
inside the data center.

As in the backbone example, we can logically conjoin these constraints
to specify the network-wide policy.
However, in addition to constraints on the shape of paths,
\sysname allows the operator to specify constraints on the BGP control plane itself.
For instance, a constraint on aggregation is included to ensure that
aggregation for global prefixes is performed from
locations inside (\In) the network to locations outside (\Out).
In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG}
(which we assume is defined earlier using an appropriate prefix such
as \CD{74.3.28.0/24})
when advertised outside the datacenter.

>>>>

Policies for (distributed) control planes differ from data-plane
policies in a few important ways. First, they must account for all failures at compile time; there is
no controller at runtime, so the routers must be configured in advance to handle failures in a compliant manner.
%
In \sysname, we enable such specifications through {\em path preferences}, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
%
Second, paths in a control-plane policy may be under-specified (e.g.,
"prefer customer" does not indicate a concrete path). The \sysname
compiler treats such under-specifications as constraints on the set of
allowed paths and automatically computes valid sets based on the topology.
%

This section introduces the \sysname language using the 
examples from the previous section.
%, introducing key aspects of
%the \sysname language along the way. 
The next section describes the complete syntax of the
language as well as our strategy for compiling it to
BGP.

@@

\sysname lets operators configure the network with the
abstraction that they have centralized control over routing.
Specifically, the operator simply provides a set of high-level constraints
that describe the
paths traffic should---or should not---take and their relative preferences.
\sysname specifications are written modularly via a series
of declarations.
%These definitions allow users to express the three
%major elements of any \sysname specification:  \emph{prefixes},
%\emph{paths} and \emph{policies}.
For example, to begin specification of the backbone
network from the previous section, we first express the idea that
we prefer that traffic leave the network through \CD{R1} over \CD{R2} (to \CD{Cust}) over \CD{Peer} over \CD{Prov} (policy P3 from Figure~\ref{fig:example1}):
%\begin{lstlisting}[mathescape=true]
%define ExitCust = $exit(R_1 \gg R_2)$
%\end{lstlisting}
\begin{code}
\Define Prefs = \Exit(R1 \Prefer R2 \Prefer Peer \Prefer Prov)
\end{code}
This  statement defines a set of \emph{ranked paths}, which includes
all paths (and only those paths) for which traffic exits our network
through either router \CD{R1}, router \CD{R2}, \CD{Peer}, or \CD{Prov}.
The paths that exit through \CD{R1}
are preferred (\Prefer) to those that exit through \CD{R2}, which are preferred to those that
leave through \CD{Peer} and then \CD{Prov}.  As we
describe in the next section, the \Exit\ predicate, as well as other
path predicates used later in this section, is simply a shorthand for
a particular regular expression over paths that is expressible in our policy
language. The preference operator (\Prefer) is flexible and can be used between constraints as well as among individual routers. For example, the above constraint could have been written equivalently as
\Exit(\CD{R1}) \Prefer \ldots \Prefer ~\Exit(\CD{Prov})

@@

\begin{code}
\Define NoTrans =
  \{\True \Path \NOT{}transit(Peer,Prov) \AND
           \NOT{}cust-transit(Cust,Prov)\}
\end{code}
\noindent
The \CD{NoTrans} constraint requires that all traffic not follow a path that transits the network between \CD{Peer} and \CD{Prov}.
Additionally, it prevents traffic from ever following paths that leave our network and later go through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
%
%% \begin{lstlisting}[mathescape=true]
%% Routing $\AND$  NoTransit
%% \end{lstlisting}
%

Collectively, the constraints above capture the entire policy. From them, our compiler will generate per-device import and export filters, local preferences,
MED attributes, and community tags to ensure that the policy is
implemented correctly under all failures.

@@

Our data center example network has three main concerns:
(1) traffic for the prefix allocated to each top-of-rack router must be able to reach that router,
(2) local services must not leak outside the data center, and
(3) aggregation must be performed on global prefixes to reduce churn
in the network.

\sysname allows modular specification of each of these constraints. The first constraint is about prefix ownership---we want traffic only for certain prefixes to end up at a particular location. The following definition captures this intent.

@@

\begin{code}
\Define Ownership =
    \{PG1 \Path \End(A)
     PG2 \Path \End(B)
     PL1 \Path \End(E)
     PL2 \Path \End(F)
     \True \Path \End(\Out)\}
\end{code}
\noindent
This definition says that traffic for prefix \CD{PG1} is allowed to follow only paths that
end at router \CD{A}; traffic for \CD{PG2},
but not \CD{PG1}, must
end at router \CD{B}; and so on.
Any traffic destined for a prefix that not a part of the data center should be allowed to leave the data center and end at some external location, which is otherwise unconstrained.
The special keyword \Out{} matches any location outside the data center network, while the keyword \In{} will match any location inside the network.

For the second constraint, we define another policy:

%% \begin{lstlisting}[mathescape=true]
%% define Routing = {
%%     $\path{p_{g*}}{any}$
%%     $\path{p_{l*}}{\NOT enter(out)}$
%%     $\path{true}{exit(out)}$
%% }
%% \end{lstlisting}
\begin{code}
\Define Locality =
    \{PL1 \OR PL2 \Path \textbf{only}(\In)\}
\end{code}
\noindent
%The first line states that there is no restriction (\Any)
%on how traffic must traverse the network for global prefixes.
%aside from the default restriction
%that traffic must not pass through the user's network and then loop
%back on itself.
%This means traffic for
%\CD{PG*} may be sent either from other data center routers or
%from external ASes.
This definition says that traffic for local
prefixes only follows paths that are internal to the network at each hop.
This constraint guarantees that the services remain reachable only to locations
inside the data center.

As in the backbone example, we can logically conjoin these constraints
to specify the network-wide policy.
However, in addition to constraints on the shape of paths,
\sysname allows the operator to specify constraints on the BGP control plane itself.
For instance, a constraint on aggregation is included to ensure that
aggregation for global prefixes is performed from
locations inside (\In) the network to locations outside (\Out).
In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG}
(which we assume is defined earlier)
when advertised outside the datacenter.
